---
title: "Portf_Draft"
author: "Brock Rowley"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(janitor)
library(ggplot2)
library(maps)
library(mapdata)
library(ggmap)
library(RColorBrewer)
library(ggrepel)

files <- list.files(here::here("data"),
                    full.names = TRUE)
files

d <- read_csv(files[1]) %>%
  clean_names()
```

Starting by looking at students score histogram.  \FloatBarrier
```{r plot_scores}
ggplot(d, aes(rit)) +
  geom_histogram(bins = 12)
```

Looking at data by disability categories.  \FloatBarrier
```{r plot_disab_cat}
ggplot(d, aes(disability_code)) +
  geom_histogram(bins = 20)
```

Starting with a simple map of the U.S  \FloatBarrier
```{r map_1, fig.width = 8, fig.height = 6}

states <- map_data("state")

usa <- ggplot() +
  geom_polygon(data = states,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = NA,
               color = "#154937") +
  coord_quickmap()
usa
```

Map of students participation across Oregon on the Alternate Assessment.  \FloatBarrier
```{r map_2, fig.width = 8, fig.height = 6}

states <- map_data("state") %>%
  rename(name = region) %>%
  select(-subregion, -group) %>%
  filter(name == "oregon")

counties <- map_data("county")
or_county <- counties %>%
  filter(region == "oregon")

or_base <- ggplot(data = states) +
  geom_polygon(aes(long, lat),
               fill = "#154937",
               color = "#55565B",
               size = 2) +
  geom_bin2d(data = d, aes(lon, lat),
             binwidth = .08) +
  scale_fill_viridis_c(option = "plasma",
                       direction = -1) +
  coord_quickmap()

or_base
```

Here is a refined map of Oregon, counties outlined for more detail.  \FloatBarrier
```{r map_3, fig.width = 8, fig.height = 6}
or_base +
  theme_void() +
  geom_polygon(data = or_county,
               aes(long, lat,
                   group = group),
               fill = NA,
               color = "#55565B")
```

Include a title and subtitle.  \FloatBarrier
```{r map_4, fig.width = 8, fig.height = 6}
or_base +
  theme_void() +
  geom_polygon(data = or_county,
               aes(long, lat,
                   group = group),
               fill = NA,
               color = "#55565B") +
  labs(title = "Student Participation by School Location in Oregon",
         subtitle = "Oregon's Extended Assessment for students with significant cognitive disabilities ")
```